---
title: "Data Import"
output: github_document
---

```{r}
library(tidyverse)
```


## Data Import: CSVs

Let's import data using the `readr` package
This is a relative path, based on where the file is on my computer.  

```{r}
read_csv("data/FAS_litters.csv")
litters_df= janitor :: clean_names(litter_df)
litters_df
```

Look at the data

```{r}
head(litters_df)
tail(litters_df)
```

The code below will give you a summary of the data

```{r}
skimr::skim(litters_df)
```



`read_csv` options...
Says which values you will consider as missing, and that you skip the first 2 rows in the data set when reading it in 

```{r}
read_csv("data/FAS_litters.csv", na = c("", "NA", 999, 88), skip=2)
```


## Other file formats

We need to read in an excel spreadsheet...

```{r}
library(readxl)
mlb.df= read_excel ("data/mlb11.xlsx")
```

## Still more formats...

Read in a SAS dataset.

```{r}
library(tidyverse)
library(readxl)
library(haven)
pulse_df= read_sas("data/public_pulse_data.sas7bdat")
pulse_df
```

## Data Export

```{r}
write_csv(lotr_words_df, file="lotr_words_df.csv")
```

## Why not base R???
```{r}
dont_do_this_df= read.csv("data/FAS_litter.csv")
```


GitIgnore is a useful to make sure that you're not saving and uploading data that shouldn't be public.  








